\chapter*{Acknowledgment}
\addcontentsline{toc}{chapter}{Acknowledgment}
\label{thanks}

First and foremost, I would like to show my gratitude to Professor Van Meter for offering me with opportunities to work on various research fields including quantum machine learning, and digital quantum simulation and distributed quantum computing, and make so many mistakes in the first three years. I could not have felt confident about progress of my knowledge and overall capabilities in the last four years if I join in any other research groups.

I also feel grateful to Professor Takahiko Satoh, who have provided me with severe and honest feedbacks about my slides and the way I make a presentation.  Without his patient support, I would not have been able to express my research topic using easy words to those who are not familiar with quantum computing.

I would also like to appreciate Professor  Michal Hajdušek, who allowed me to work on a digital quantum simulation about quantum synchronization between two spin-1 particles.  Even though understanding the setting itself is a really hard work, it is my honor to work on quantum physics, which is my long-time favorite since when I was in high school.  I will resume this joint research after I start my Master's.

I also appreciate Professor Masashi Aono, who taught me the basics of optimization theory and complex system in his lectures.  I would not have thought about working on combinatorial optimization for my graduation thesis, and quantum synchronization for the other research, if I didn't take his intriguing lectures.

I also thank other members in AQUA, especially Ryosuke Satoh for mentoring my research work in this entire year and taking care of me in various aspects, Naphan Benchasattabuse for always giving me critical feedbacks after my progress report, Yasuhiro Okura for suggesting me the details of this research topic, Taaki Matsuo for treating me so many times, Nozomi Tanetani for keeping encouraging me when I felt devastated in the Mitou Target, and Shigetora Miyashita for having a thoughtful conversation about modern physics.

Last but not least, I would like to express my deepest gratitude to my family members who have raised me and become supportive in any situations.  
%%% Local Variables:
%%% mode: japanese-latex
%%% TeX-master: "../yummy_bthesis"
%%% End:
